Placeholder

### 2021-02-13 Paper_Histograms.Rmd
Changed OCDs to OCDRs in the retro diagnosis graph

dat.retro_OCD_by_sample <- dat.retro_OCD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("OCDs" = n())

@@

dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)

>>>>

dat.retro_OCD_by_sample <- dat.retro_OCD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("OCDRs" = n())

@@

dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDRs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)
